Network Configuration Synthesis with Abstract Topologies

### 2016-11-07 paper/abstraction/appendix.tex
update language equivalence proof for appendix

     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,G) 
        & = & \textbf{if}~ ns_1 = G.s ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
        &   & \textbf{else}~ n_1 : ( con({ns}_1,\ell,\Gamma,G), n_2) \rightarrow (con({ns}_2,\ell,\Gamma,G),n_3)

@@

\[ \begin{array}{ll}
  \text{Product Graph nodes} & n,m,o \\
  \text{Topology locations} & a,b,c \\
  \text{Automata states} & q_i \\
  \text{Topologies} & G, G^A \\
  \text{Product Graph} & PG, PG^A \\
  \text{Automata} & M_i, M_i^A \\
\end{array} \]

@@

\begin{defn}
If $r$ complies to state machine $M^A$, then we compile the policy $con(r)$ in the following way:

  \[ \begin{array}{ll}
    1. & \sigma^A(q,f(l)) = q' \iff \sigma(q,l) = q' \\
    2. & q \in F^A \iff q \in F \\
  \end{array} \]

That is, we construct a new automata over the same states and final states, but with a different transition function $\sigma$. This ensures that there is a bisimulation between the two state machines.

\end{defn}

\begin{lem}
  $M^A$ matches $f(p)$ $\iff$ $M$ matches $p$.
\end{lem}

\begin{proof}
  Suppose $M^A$ matches $f(p) = A_1, \dots, A_k$, then there exists a trace through $M^A$ of the form:

  $$q_0, q_1, \dots, q_{k+1}$$

  where $\sigma^A(q_i, A_i) = q_{i+1}$ and $q_{k+1} \in F^A$. We must show that $M$ matches $p = a_1, \dots, a_k$.

  From the construction of the automaton, we know that $\sigma(q_i, a_i) = q_{i+1}$ and $q_{k+1} \in F \iff q_{k+1} \in F^A$. Therefore, the trace $q_0, q_1, \dots, q_{k+1}$ is accepted by $M$. 
  %
  The same proof is symmetric for the other direction.
\end{proof}

\begin{thm}
  $M$ matches $p$ $\iff$ $p \in \Lang(con(r))$
  \begin{proof}
    \[ \begin{array}{lllr}
      M ~\text{matches}~ p &\iff& M^A ~\text{matches}~ f(p) & \textit{previous lemma} \\
                         &\iff& f(p) \in \Lang(r) & \textit{automaton construction} \\
                         &\iff& p \in \Lang(con(r)) & \textit{first lemma} \\
    \end{array} \]

  \end{proof}
\end{thm}

>>>>

     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,G) 
        & = & \textbf{if}~ ns_1 = \{G.s\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
        &   & \textbf{else}~ n_1 : ( con({ns}_1,\ell,\Gamma,G), n_2) \rightarrow (con({ns}_2,\ell,\Gamma,G),n_3)

@@

\[ \begin{array}{ll}
  \text{Product Graph nodes} & n,m,o \\
  \text{Topology locations} & a,b,c \\
  \text{Automata states} & q_i \\
  \text{Topologies} & G, G^A \\
  \text{Product Graph} & PG, PG^A \\
  \text{Automata} & M, M^A \\
\end{array} \]

@@

%\begin{defn}
%If $r$ complies to state machine $M^A$, then we compile the policy $con(r)$ in the following way:%

%  \[ \begin{array}{ll}
%    1. & \sigma^A(q,f(l)) = q' \iff \sigma(q,l) = q' \\
%    2. & q \in F^A \iff q \in F \\
%  \end{array} \]%

%That is, we construct a new automata over the same states and final states, but with a different transition function $\sigma$. This ensures that there is a bisimulation between the two state machines.%

%\end{defn}%
%

%\begin{lem}
%  $M^A$ matches $f(p)$ $\iff$ $M$ matches $p$.
%\end{lem}%

%\begin{proof}
%  Suppose $M^A$ matches $f(p) = A_1, \dots, A_k$, then there exists a trace through $M^A$ of the form:%

%  $$q_0, q_1, \dots, q_{k+1}$$%

%  where $\sigma^A(q_i, A_i) = q_{i+1}$ and $q_{k+1} \in F^A$. We must show that $M$ matches $p = a_1, \dots, a_k$. %

%  From the construction of the automaton, we know that $\sigma(q_i, a_i) = q_{i+1}$ and $q_{k+1} \in F \iff q_{k+1} \in F^A$. Therefore, the trace $q_0, q_1, \dots, q_{k+1}$ is accepted by $M$. 
%  %
%  The same proof is symmetric for the other direction.
%\end{proof}%
%

%\begin{lem}
%  $M$ matches $p$ $\iff$ $p \in \Lang(con(r))$
%  \begin{proof}
%    \[ \begin{array}{lllr}
%      M ~\text{matches}~ p &\iff& M^A ~\text{matches}~ f(p) & \textit{previous lemma} \\
%                         &\iff& f(p) \in \Lang(r) & \textit{automaton construction} \\
%                         &\iff& p \in \Lang(con(r)) & \textit{first lemma} \\
%    \end{array} \]%

%  \end{proof}
%\end{lem}

\begin{lem}
  Consider the PG created from compiling the constraint $p = (t ~\Path~ r_1 ~\Prefer~,\dots, ~\Prefer~ r_k)$ with state machine $M^A_i$ for each $r_i$. We know that, for each $(pfx ~\Path~ r'_1 ~\Prefer~,\dots, ~\Prefer~ r'_k) \in con(p)$ where $r'_i$ is of the form $r \cap \text{end}(L)$ we can constuct state machine $M_i$ for $r'_i$ in the following way:

    \[ \begin{array}{lll}
      1. & \sigma(q_0,l) = q' \iff \sigma^A(q,f(l)) = q' & \textbf{for each}~~ l \in L \\
      2. & \sigma(q,l) = q' \iff \sigma^A(q,f(l)) = q' & \textbf{for each}~~ l \in \Sigma \\
      3. & q \in F \iff q \in F^A & \\
    \end{array} \]

  then $M_i$ matches $p$ $\iff$ $p \in \Lang(r_i')$

  \vspace{1em}
  \begin{proof} by cases on $t$

    \vspace{1em}

    \textbf{Case} $(\$x ~\Path~ r_1 ~\Prefer~,\dots, ~\Prefer~ r_k)$

    \[ \begin{array}{lcl}
      con(p) &=& pfx_1 ~\Path~ con(r_1) \cap \text{end}(l_1), ~\Prefer~ \dots ~\Prefer~ con(r_k) \cap \text{end}(l_1)  \\
             & & \dots, \\
             & & pfx_n ~\Path~ con(r_1) \cap \text{end}(l_n), ~\Prefer~ \dots ~\Prefer~ con(r_k) \cap \text{end}(l_n)
    \end{array} \]

    Case ($\Rightarrow$)

    Assume $M_i$ matches $p$. Then this means that $M^A_i$ matches $f(p)$. If we have a trace of string of the form $ p = x_1 \cdot \dots \cdot x_n$, then $f(p) = f(x_1) \cdot \dots \cdot f(x_n)$. For each transition $\sigma(q,l) = q'$ in the concrete automaton, we have transition $\sigma(q,f(l)) = q'$ in the abstract automaton, and they have the same final states, so this trace is accepting for $M^A_i$. Because $M^A_i$ matches $f(p)$, this means that $f(p) \in \Lang(r_i)$. From our above lemma, this means that $p \in \Lang(con(r_i))$. We also know that, since $L = \{ l_i \}$, the first transition $\sigma(q_0,l_i)$ is the only transition allowed from the initial state for $M_i$. So this means that $p \in \Lang(\text{end}(l_i))$. Since we know that $p \in \Lang(con(r_i))$ and $p \in \Lang(\text{end}(l_i))$, we know that $p \in \Lang(con(r_i) \cap \text{end}(l_i))$ and thus $p \in \Lang(r'_i)$.

    \vspace{1em}
    Case ($\Leftarrow$)

    Assume $p \in \Lang(r'_i)$. This means that $p \in \Lang(con(r_i) \cap \text{end}(l_i))$. In turn, this means that $p \in \Lang(con(r_i))$ and $p \in \Lang(\text{end}(l_i))$. From the above lemma, we know that $f(p) \in \Lang(r_i)$, which means that $M^A_i$ matches $f(p)$. 
    %
    Consider any string of the form $p = l_i \cdot x_2 \cdot \dots \cdot x_n$ such that $p \in \Lang(con(r_i) \cap \text{end}(l_i))$. Clearly there is a transition defined for $\sigma(q_0,l_i) = q_1$.
    %
    This means that $M^A_i$ matches $f(l_i) \cdot f(x_2) \cdot \dots \cdot f(x_n)$
    %
    For each transition $\sigma^A(q,f(x_i)) = q'$, we have $\sigma(q,x_i) = q'$ in $M_i$.
    %
    Thus the string $l_i \cdot x_2 \cdot \dots \cdot x_n$ is accepted along the same path of automaton states.

  \vspace{1em}

  \textbf{Case} $(pfx ~\Path~ r_1 ~\Prefer~,\dots, ~\Prefer~ r_k)$

    \[ \begin{array}{lcl}
      con(p) &=& pfx_1 ~\Path~ con(r_1) \cap \text{end}(\Sigma^*), ~\Prefer~ \dots ~\Prefer~ con(r_k) \cap \text{end}(\Sigma^*) \\
    \end{array} \]

    First we observe that: $M^A_i$ matches $f(p)$ $\iff$ $M_i$ matches $p$.
    %
    Suppose $M^A_i$ matches $f(p) = A_1, \dots, A_k$, then there exists a trace through $M^A_i$ of the form:%
    %
    $q_0, q_1, \dots, q_{k+1}$
    %
    where $\sigma^A_i(q_i, A_i) = q_{i+1}$ and $q_{k+1} \in F^A$. We must show that $M_i$ matches $p = a_1, \dots, a_k$. %
    %
    From the construction of the automaton, we know that $\sigma_i(q_i, a_i) = q_{i+1}$ and $q_{k+1} \in F \iff q_{k+1} \in F^A_i$. Therefore, the trace $q_0, q_1, \dots, q_{k+1}$ is accepted by $M_i$. 
    %
    The same proof is symmetric for the other direction. It follows that:

    \[ \begin{array}{lll}
      M ~\text{matches}~ p &\iff& M^A ~\text{matches}~ f(p) \\
                         &\iff& f(p) \in \Lang(r) \\
                         &\iff& p \in \Lang(con(r)) \\
    \end{array} \]%

\end{lem}
